\begin{frame}
\frametitle{Operations: three kinds}

\begin{itemize}
  \item \textbf{\hh-BLAS1\&2:} Assembly, AXPY, GEMV \newline
        Simple. Operating only on leaves.
  \item \textbf{\hh-BLAS3:} GEMM, TRSV \newline 
        More involved. Operations at many different levels of the same sub-tree.
  \item \textbf{\hh-LAPACK:} Inverse, $LU$, $LL^T$.\newline
        Uses BLAS2 and BLAS3 operations, harder to implement in parallel.
\end{itemize}

\begin{block}{Base operations}
All operations use BLAS/LAPACK. Typical subroutines are: SVD, QR, 
LU, TRSV, GEMM and GEMV.
\end{block}
\end{frame}

%%%

\begin{frame}
\frametitle{Computation details}
\begin{block}{Typical issues}
The \hmat algorithms are not nice for the hardware:
\begin{itemize}
\item Very small operations; 
\item Oddly-shaped matrices: "Tall \& skinny";
\item High memory band.
\end{itemize}
\end{block}

\begin{block}{Observations}
  \begin{itemize}
    \item Most (70-80\%) of the time spent in: 
    \begin{itemize}
      \item QR decompositions of T\&S matrices; 
      \item SVD decompositions of small matrices.
    \end{itemize}
    \item BLAS implementions cannot reach the peak performance;
    \item Very high memory bandwidth.
  \end{itemize}
\end{block}
\end{frame}

%%%

\begin{frame}
\frametitle{Complexity estimates}

\begin{alert}{Useful pointers}
\begin{itemize}
\item Most complexity estimates assume a fixed upper bound $k$ for the 
low-rank matrices involved;
\item The structure of the matrix (as represented by a tree) is 
important as well: a large depth with small blocks is typically a bad omen.
\end{itemize}
\end{alert}

\begin{block}{Common operations}
For a matrix size of $N \times N$ with the previous assumptions:
\begin{itemize}
\item assembly:  time and storage is in $\mathcal{O}(kN \log N)$;
\item addition: $\mathcal{O}(k^2N \log N )$ operations;
\item multiplication and Cholesky factorisation: $\mathcal{O}(k^3 N \log^3 N )$ operations;
\item \textcolor{red}{in practice a $\mathcal{O}(N \log^2 N)$ complexity is observed.}
\end{itemize}
\end{block}

\end{frame}

